\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}

\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Michael Horvath}}\\
	San Diego, CA $\cdot$ michaelhorvath87@gmail.com $\cdot$ 845-309-4388 $\cdot$ github.com/kwisatzheadache\\
\end{center}

\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{University of Kansas}\hfill Lawrence, KS\\
BS Psychology and Statistics \textit{GPA: 3.6} \hfill Grad: May 2011\\
\vspace{2mm}

\vspace*{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Embrace Healthwear} \hfill San Diego, CA\\
\textit{Software Engineer} \hfill Sept, 2017 | Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Data analysis and machine learning for motion sensor signal data, with emphasis on seamless pipelining and mapping research literature to procedural findings. Data preprocessing, vectorization and feature engineering in preparation for supervised and unsupervised classification. Python, binary classification, time-series analysis, database engineering, mysql, principal component analysis.
\end{itemize}

\textbf{Personal Projects}\\
\hfill Jan 2017 | Aug 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed a neural net constructor from the ground up in Elixir, to improve understanding of machine learning at its most basic level. Applied constructor to solve Rubiks cube.
	\item Trained Long Short Term Memory network on cryptocurrency data to predict market volatility. Wrote trading algorithm based on machine learning predictions.
	\item Deployed various machine learning programs, ranging from style-transfer to binary-classification, regression, and multi-class classification, on Google Cloud Computing platform to evaluate performance across various hyperparameters. Explored optimal neural net configurations and validation techniques.
\end{itemize}

\textbf{University of Kansas} \hfill Lawrence, KS\\
\textit{Program Evaluation Consultant} \hfill Sep 2010 | May 2011\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Reconstructed the ARC Self-Determination Scale - a 72 item self-report metric for use in reporting self-determination among students with learning disabilities. Presented findings to authors and collaborators. New version, with shortened length and increased validity and reliability is included in the latest iteration of the National Longitudinal Transition Study (NLTS-2), administered by the Department of Education.
	\item Collaborated with Program Evaluation Team to assess and evaluate various inter-departmental education grants for the purpose of grant submission, evaluation, and renewal.
	\item Developed, deployed, and administered training grant evaluation surveys, gathering outcome data concerning program success and student outcomes.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming languages: & Python, Elixer, JS, Node                              \\
	Statistics:            & Regression, ANOVA, SAS, SPSS, MPLUS                   \\
	Machine Learning:      & Classification, PCA, time-series, feature engineering \\
\end{tabular}

\vspace*{2mm}

        

\vspace*{2mm}

\header{Awards}
\textbf{CalTech Signature Award} \hfill Kansas City, KS\\
Innovative and Creative thinking in mathematics and sciences. \hfill May 2006\\
\vspace*{2mm}
\textbf{National Merit Scholar}\\
Outstanding academic and extra-curricular achievement. \hfill 2006\\
\vspace*{2mm}

\ 
\end{document}